Bird beak's elaboration and exploration

### 2022-10-20 Analysis/11-variance_partitioning.Rmd
Update 11-variance_partitioning.Rmd

```{r, echo = FALSE}
par(mar = c(5, 6, 4, 2) + 0.1)
var_table <- MCMCglmm.variance(test, scale = FALSE)
colnames(var_table) <- c("phylogeny", "residuals")
boxplot(var_table, horizontal = TRUE, las = 1, xlab = "Variance")
abline(v = var(data$variable), col = "red", lwd = 2)
legend("topright", col = "red", lwd = 2, lty = 1, legend = "Observed variance")
```

>>>>

```{r, echo = FALSE}
par(mar = c(5, 6, 4, 2) + 0.1)
var_table <- MCMCglmm.variance(test, scale = FALSE)
colnames(var_table) <- c("phylogeny", "residuals")
boxplot(var_table, horizontal = TRUE, las = 1, xlab = "Variance")
abline(v = var(data$variable), col = "red", lwd = 2)
legend("topright", col = "red", lwd = 2, lty = 1, legend = "Observed variance")

## Adding the cophenetic variance line?
coph <- cophenetic(tree)
coph_var <- sd(coph)^2
scaled_var <- sd(coph * data$variable)^2
```
